
---
title: "Getting Started with metaverse"
author: "Mahmood Ahmad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with metaverse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

# Introduction

The metaverse package provides state-of-the-art methods for robust meta-analysis.

## Installation

```{r eval=FALSE}
# Install from GitHub
devtools::install_github("mahmood726-cyber/metaverse")
```

## Basic Usage

```{r}
library(metaverse)

# Simulate data
set.seed(123)
data <- simulate_meta_data(k = 30, theta = 0.5, tau2 = 0.1)

# Robust meta-analysis
result <- meta_robust(data$yi, data$vi, method = "MM")
print(result)
```

## Advanced Features

### Contamination Models

Handle outliers with contamination models:

```{r}
# Add contamination
data_contam <- simulate_meta_data(k = 30, contamination = 0.2)

# Fit with t-mixture model
result_contam <- meta_robust(data_contam$yi, data_contam$vi, 
                           contamination = "t-mixture")
```

### Variable Selection

Select important moderators:

```{r}
# Generate data with moderators
data_mod <- simulate_meta_data(k = 50, moderators = 5)

X <- as.matrix(data_mod[, grep("mod", names(data_mod))])

# Knockoff filter
selected <- select_moderators(X, data_mod$yi, data_mod$vi, 
                             method = "knockoff", fdr = 0.1)
print(selected)
```

## Visualization

Create publication-quality plots:

```{r eval=FALSE}
# Forest plot
forest_plot(result)

# Funnel plot
funnel_plot(result)
```

## Sensitivity Analysis

Comprehensive sensitivity analyses:

```{r eval=FALSE}
# Create model object
model <- new("metaverse", data = data, robust = result)

# Run sensitivity analyses
sensitivity <- assess_sensitivity(model, analyses = "all")
```

