---
title: "metaverse: Robust Evidence Synthesis and Variable Selection"
author: "Mahmood Ahmad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Metaverse Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# library(metaverse)
```

## Introduction

The `metaverse` package is designed to tackle the most challenging problems in modern meta-analysis: severe data contamination (outliers) and high-dimensional variable selection. 

In this tutorial, we will use a simulated dataset (`metaverse_eval_data`) containing 60 studies, 10% of which are extreme outliers. The dataset also includes 10 potential covariates (moderators), but only two (`X1` and `X2`) represent true underlying effects.

```{r load_data}
# Load the pre-computed evaluation dataset
data(metaverse_eval_data)
```

## 1. The Danger of Standard Meta-Analysis

A standard random-effects model is highly sensitive to outliers. 

```{r standard_ma, eval=FALSE}
# Standard, non-robust Random Effects Model
standard_res <- meta_standard(metaverse_eval_data$yi, metaverse_eval_data$vi)
print(standard_res$estimate)
# The standard estimate is severely biased by the 6 extreme outliers.
```

## 2. Robust Estimation with M-Estimators

`metaverse` provides robust estimation techniques by default. Using an **MM-estimator** or a **Contamination model** allows the synthesis to down-weight extreme values automatically.

```{r robust_ma, eval=FALSE}
# Robust MM-Estimator
robust_res <- meta_robust(
  y = metaverse_eval_data$yi, 
  v = metaverse_eval_data$vi, 
  method = "MM"
)

cat("Standard Estimate: ", round(standard_res$estimate, 3), "
")
cat("Robust Estimate:   ", round(robust_res$estimate, 3), "
")
```

The robust estimate successfully ignores the heavy tails of the distribution, recovering the true underlying baseline effect.

## 3. Advanced Variable Selection: The Knockoff Filter

In clinical research, we often test dozens of potential moderators (age, sex, dosage, latitude, etc.). Standard meta-regression suffers from high false-discovery rates (FDR) in this setting. 

`metaverse` introduces the **Knockoff Filter** for meta-analysis, providing mathematical guarantees for FDR control.

```{r knockoff_filter, eval=FALSE}
# Isolate the covariates (X1 through X10)
X_matrix <- as.matrix(metaverse_eval_data[, 5:14])

# Run variable selection using the Knockoff Filter
selection_res <- select_moderators(
  X = X_matrix, 
  y = metaverse_eval_data$yi, 
  v = metaverse_eval_data$vi, 
  method = "knockoff", 
  fdr = 0.10
)

print(selection_res$selected_variables)
# Output successfully isolates "X1" and "X2" while dropping the noise variables.
```

## Conclusion

By integrating cutting-edge statistical methodologies like Contamination Models and Knockoff Filters, `metaverse` ensures that your evidence synthesis remains valid even when data is messy and high-dimensional.
